EEOB563 -- Assignment #3

### 2019-02-21 assignments/3/assignment_3.Rmd
Rendered assignment

---
title: 'EEOB563 -- Assignment #3'
author: "Dennis Psaroudakis"
date: "February 20th 2019"
output:
  pdf_document:
    dev: pdf
    latex_engine: lualatex
    md_extensions: +link_attributes+multiline_tables
    pandoc_args: --listings
mainfontoptions: Numbers=OldStyle
monofont: Linux Libertine Mono O
mainfont: Linux Libertine O
papersize: letter
sansfont: Linux Biolinum O
language: en-US
titlepage: true
...

@@

## 5

>>>>

---
title: 'EEOB563 -- Assignment #3'
author: "Dennis Psaroudakis"
date: "February 20th 2019"
output:
  pdf_document:
    dev: pdf
    latex_engine: lualatex
    md_extensions: +link_attributes+multiline_tables
    pandoc_args: --listings --colorlinks
mainfontoptions: Numbers=OldStyle
monofont: Linux Libertine Mono O
mainfont: Linux Libertine O
papersize: letter
sansfont: Linux Biolinum O
language: en-US
titlepage: true
...

@@

## 5
I used the mafft alignment for this one because I somehow didn't trust the Pal2Nal result. No, the trees are not the same:

![Majority consensus tree](majTree.png){width=60%}

![Strict consensus tree](strictTree.png){width=60%}

Their topology is different and even more importantly the majority consensus tree contains distances while the strict consensus tree does not.
